---
title: "virus 2"
output: html_document
date: '2022-06-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
newdata<- read.csv(file="clinicalTrial2.csv")
```

```{r eval=FALSE}
newdata <- newdata %>%
mutate(across(where(is.character), as.factor))
```

# Descriptive Results



## Graphical Descriptive Results

```{r}
barchartGC(~infected + vaxStatus,data=newdata)
barchartGC(~infected + vaxStatus,data=newdata, type="percent")

```

The bar charts above show a graphical representation of the relationship between vaccination status and covid infection status among a group of people. Based on the charts, we can see that the frequency of testing positive of covid is significantly less among people who got the first vaccine, the new vaccine, and both the first and new vaccine. Meanwhile, for people who did not get either of the two vaccines, there is comparably a higher frequency and percentage of covid infection.  



## Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + vaxStatus, data=newdata)
rowPerc(table1)
colPerc(table1)
```

To find out if the previous bar charts would provide statistical significance, a new test summarized by the table above shows the actual numerical values of the percentages of infection among people with various vaccination status. As seen above, majority of the people who got infected with covid are those who did not get either of the two vaccine. Specifically, 63.93% of this population is made up of people who received no vaccines of any kind. Furthermore, the infection among people who got both the first and new vaccines is less than getting just one of the two vaccines. There are only 6.95% of people who got both the first and new vaccine who got infected with covid, which is a smaller value compared to the 21.62% for people who got the first vaccine and 8.49% for people who got the new vaccine only. Therefore, the numerical descriptive results show that there is less infection among people who got either or both the vaccines than none at all. 



# Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1, simulate.p.value = TRUE)

```

Seeing that the p value of the chi-squared test above is very small, another test comparing two data at a time would be added to supplement the results. 

```{r}
fisherXY = function(x, y, confL = 0, printAll=TRUE){
  # Inputs: 
  #   x: factor variable, 2 levels
  #   y: factor variable, n levels
  # confL: confidence level, default = 0.95
  #        print only those tables, results if p-value < (1-confL)
  # printAll: overide the 'print only if p-value < (1-confL), and
  #           print all tables and fisher test results
  #
  # Constraint:
  #   x and y must be same length
  #
  # Outputs:
  #   All 2x2 Fisher exact tests
  
  if(confL<0 || confL> 1){
    print('error: confL must be between 0 and 1')
    return(999)
  }
  
  if(!is.factor(x)) x=as.factor(x)
  if(!is.factor(y)) y=as.factor(y)
  
  fisherTable = as.matrix(table(x, y))
  cat('\ncontingency table:\n')
  print(fisherTable)
  cat('\n***All 2X2 tests****\n\n')

  # all 2x2 tests
  levelsY = levels(y)
  levelsX = levels(x)
  
  m = length(levelsX)
  n = length(levelsY)
  
  confLevel = 0.95
  if (confL !=0 ) confLevel=confL
  
  for (i in 1:(m-1))
       for(j in ((i+1):m))
          for (k in 1:(n-1))
             for (l in ((k+1):n)) {
                
                 fisherIndexX = c(i,j)
                 fisherIndexY = c(k,l)
                 
                 fTempTable = as.matrix(fisherTable[fisherIndexX,
                                        fisherIndexY])
                 
                 fisherTest=fisher.test(fTempTable, conf.int = TRUE, 
                              conf.level = confLevel)
                 
                 if((fisherTest$p.value < (1-confLevel) ) || printAll){
                   
                       print(c(levelsX[i], levelsX[j]))
                       print(c(levelsY[k], levelsY[l]))
                       print(fTempTable)
                       print(fisherTest)
                       cat('\n')
                 }
                 
        }
}

```
```{r}
fisherXY(newdata$infected,newdata$vaxStatus)
```

Comparing two vaccination status at a time, we can see which vaccination status holds a better chance in preventing covid infection based on the p-values of each test. The p-values above confirms what has been observed earlier that people who get both the first and new vaccine have lower infection compared to getting no vaccines at all. Since the p-values of the tests above are low, we can claim that the first and new vaccine combined are better than getting either one of the vaccines and significantly much better than getting no vaccine of any kind. However, there is one test that had a high p-value, and that is the comparison between first&new and new. This means that these two vaccination status were not statistically different.  




